Minimal trap-spaces of Logical models are maximal siphons of their Petri-net encoding

### 2022-04-29 cmsb22.tex
A little something everywhere

\section{Minimal trap-spaces as maximal siphons}
\subsection{Preliminaries}
\subsubsection{Traps-spaces}
\subsubsection{Petri-net encoding of Logical models}

Original encoding~\cite{chaouiya2011petri} vs. more recent one~\cite{chatain2014characterization}

@@

SBML-Qual~\cite{chaouiya2013sbml}/BoolNet~\cite{mussel2010boolnet,klarner2017pyboolnet} to PNML\footnote{\url{https://www.pnml.org/}} works via GINsim/BioLQM~\cite{chaouiya2012logical} with
\begin{verbatim}
\verb|java -jar GINsim.jar -lqm <input.sbml/input.bnet> <output.pnml>|
\end{verbatim}

\section{Evaluation}
\subsection{Benchmark vs. implicant-based methods}
\subsection{Detailed biological example}

>>>>

\section{Minimal trap-spaces as maximal siphons}
\subsection{Preliminaries}
\subsubsection{Traps-spaces}

\cite{klarner2015computing,klarner2017pyboolnet,cifuentes2020control}

\subsubsection{Petri-net encoding of Logical models}

Original encoding~\cite{chaouiya2004qualitative,chaouiya2011petri} vs. more recent one~\cite{chatain2014characterization}.
All identical on Boolean models?

@@

SBML-Qual~\cite{chaouiya2013sbml}/BoolNet~\cite{mussel2010boolnet,klarner2017pyboolnet} to PNML\footnote{\url{https://www.pnml.org/}} works via GINsim~\cite{chaouiya2012logical}/BioLQM\footnote{http://www.colomoto.org/biolqm/} with
\begin{verbatim}
java -jar GINsim.jar -lqm <input.sbml/input.bnet> <output.pnml>
\end{verbatim}

\section{Evaluation}
\subsection{Benchmark vs. implicant-based methods}

\url{http://colomoto.org/biolqm/doc/tools-trapspace.html}

\subsection{Detailed biological example}

TBD
